Learning to Dispatch: A Reinforcement Learning Framework for Train Dispatch Networks

### 2025-04-21 paper/main.tex
Add NN comparison figure

\documentclass[runningheads]{llncs}
\usepackage{xcolor}
\usepackage{url}
\usepackage{graphicx} 
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, fit}

@@

>>>>

\documentclass[runningheads]{llncs}
\usepackage{xcolor}
\usepackage{url}
\usepackage{graphicx} 
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usetikzlibrary{arrows.meta, positioning, fit}

@@

\begin{figure}[htbp]
    \centering

    % ANN
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8,
            input/.style={circle,draw=blue!50,fill=blue!20,thick,minimum size=1.2em},
            hidden/.style={circle,draw=black!60,fill=black!10,thick,minimum size=1.2em},
            output/.style={circle,draw=red!70,fill=red!20,thick,minimum size=1.2em}
        ]
            % Input Layer
            \foreach \i in {1,...,3}
                \node[input] (I\i) at (0,-\i) {};

            % Hidden Layer
            \foreach \i in {1,...,4}
                \node[hidden] (H\i) at (2,-\i+0.5) {};

            % Output Layer
            \foreach \i in {1,...,2}
                \node[output] (O\i) at (4,-\i-0.5) {};

            % Connections
            \foreach \i in {1,...,3}
                \foreach \j in {1,...,4}
                    \draw[->] (I\i) -- (H\j);

            \foreach \i in {1,...,4}
                \foreach \j in {1,...,2}
                    \draw[->] (H\i) -- (O\j);
        \end{tikzpicture}
        \caption{Fully Connected ANN}
    \end{subfigure}
    \hfill

    % CNN
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
            \begin{tikzpicture}[
                image/.style={draw, rounded corners, fill=blue!20, minimum width=2.5cm, minimum height=2.5cm},
                filter/.style={draw, thick, fill=red!20, minimum width=1cm, minimum height=1cm},
                feature/.style={draw, thick, fill=green!20, minimum width=1cm, minimum height=2cm},
                ann/.style={draw, thick, fill=purple!20, circle, minimum size=1cm},
                arrow/.style={->, thick, >=Stealth},
                every node/.style={font=\small}
            ]

            % Nodes
            \node[image] (input) at (0, 0) {\includegraphics[width=2.5cm]{example-image}};
            \node[filter] (filter) at (0, -2.5) {};
            \node[feature] (feature) at (0, -5) {};
            \node[ann] (ann) at (0, -7.5) {NN};

            % Labels
            \node[right] at (input.east) {28x28 Image};
            \node[right] at (filter.east) {3x3 Filter};
            \node[right] at (feature.east) {Pooled Features};
            \node[right] at (ann.east) {Neural Network};

            % Arrows
            \draw[arrow] (input) -- (filter);
            \draw[arrow] (filter) -- (feature);
            \draw[arrow] (feature) -- (ann);

            \end{tikzpicture}
            \caption{Convolutional Neural Network (CNN)}
    \end{subfigure}
    \hfill

    % GNN
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
            \begin{tikzpicture}[
                node/.style={circle, draw, fill=orange!30, minimum size=1cm},
                message/.style={draw, thick, fill=blue!20, minimum width=1.5cm, minimum height=0.8cm, rounded corners},
                aggregate/.style={draw, thick, fill=green!20, minimum width=1.5cm, minimum height=0.8cm, rounded corners},
                arrow/.style={->, thick, >=Stealth},
                doublearrow/.style={<->, dotted, thick, >=Stealth},
                every node/.style={font=\small}
            ]

            % Nodes
            \node[node] (A) at (0, 0) {A};
            \node[node] (B) at (2, 1.5) {B};
            \node[node] (C) at (2, -1.5) {C};
            \node[node] (D) at (4, 0) {D};

            % Edges
            \draw[doublearrow] (A) -- (B);
            \draw[doublearrow] (A) -- (C);
            \draw[doublearrow] (B) -- (D);
            \draw[doublearrow] (C) -- (D);

            % Message Passing
            \node[message] (msg) at (2, -3) {Message Passing};
            \draw[arrow] (C) -- (msg);
            \draw[arrow] (A) -- (msg);
            \draw[arrow] (D) -- (msg);

            % Aggregation
            \node[aggregate] (agg) at (2, -4.5) {Aggregation};
            \draw[arrow] (msg) -- (agg);
            % Pooling
            \node[aggregate] (pooling) at (2, -6) {Pooling};
            \draw[arrow] (agg) -- (pooling);

            % Output
            \node[node, fill=purple!30] (output) at (2, -7.5) {NN};
            \draw[arrow] (pooling) -- (output);
            \end{tikzpicture}
            \caption{Graph Neural Network (GNN) with Message Passing and Aggregation Steps}
    \end{subfigure}

    \caption{Simplified visual comparison of common neural network architectures}
\end{figure}
